---
title: "DataFest 2022"
author: "Yixiao (Carl) Cao "
date: "4/2/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
rm(list=ls(all=TRUE))
```

```{r}
require(runjags)
```

Assume individual $j$ played $n_j$ games, and at the $i^{th}$ game their play time is $Y$. Then the play time for each individual at each game follows a normal distribution which we assume have an observation specific mean and a shared variance:
$$Y_{ij}\sim\text{Normal}(\mu_{ij},\sigma)$$
where $j = 1, 2, ... 166$ and $i = 1, 2, ... n_j$.

We let $x_i$, the index of the game, be the only predictor in a linear model of $\mu_{ij}$, that is:
$$\mu_{ij} = \beta_{0j}+\beta_{1j}*x_i$$
Notice that $\mu_ij$ is deterministic, that is, determined by $\beta_{0j}$ and $\beta{1j}$. So $\mu_{ij}$ is not a parameter to be estimated, but the $beta$'s are. The Bayesian hierarchical model suggests that each $\beta_{0j}$ and $\beta_{1j}$ are different (on an individual level) but related (they share the same prior).
That is,
\begin{align*}
\beta_{oj}&\sim\text{Normal}(\mu_0, s_0)\\
\beta_{1j}&\sim\text{Normal}(\mu_1, s_1)\\
1/\sigma^2&\sim\text{Gamma}(a,b)\\
\end{align*}

```{r}
modelString <- "
model {
for (i in 1:N){
y[i] ~ dnorm(beta0 + beta1*x[i], invsigma2)
}

# priors
beta0 ~ dnorm(mu0, g0)
beta1 ~ dnorm(mu1, g1)

invsigma2 ~ dgamma(a, b)
sigma <- sqrt(pow(invsigma2, -1))
}
"
```

```{r}
all_players <- read.csv("all_players 1.csv")
```

```{r}
id <- 6427004
player_data <- all_players[all_players$player_id == id, ]
rownames(player_data) <- 1:nrow(player_data)
y <- as.vector(player_data$play_time)
x <- as.vector(1:nrow(player_data))
N <- length(y)
the_data <- list("y" = y, "x" = x, "N" = N, 
                 "mu0" = 0, "g0" = 0.0001,
                 "mu1" = 0, "g1" = 0.0001,
                 "a" = 1, "b" = 1)

initsfunction <- function(chain){
  .RNG.seed <- c(1,2)[chain]
  .RNG.name <- c("base::Super-Duper",
  "base::Wichmann-Hill")[chain]
  return(list(.RNG.seed=.RNG.seed,
              .RNG.name=.RNG.name))
}
```

```{r}
posterior <- run.jags(modelString,
                      n.chains = 1,
                      data = the_data,
                      monitor = c("beta0", "beta1", "sigma"),
                      burnin = 1000,
                      sample = 1000,
                      thin = 1,
                      inits = initsfunction)
```
```{r}
summary(posterior)
```

```{r}
plot(posterior, vars = "beta1")
```
```{r}
beta1_vec <- posterior$mcmc[[1]][,2]
```

```{r}
beta1_dist <- as.data.frame(matrix(nrow=1000,ncol=1))
id <- "15"
beta1_dist$id<-beta1_vec

```

```{r}
unique(all_players$player_id)
```

```{r}
jags_on_all <- function(all_players){
  all_id <- unique(all_players$player_id)
  k <- length(all_id)
  beta1_dist <- as.data.frame(matrix(nrow = 500))
  for (i in 1:k){
    id <- all_id[i]
    player_data <- all_players[all_players$player_id == id, ]
    rownames(player_data) <- 1:nrow(player_data)
    y <- as.vector(player_data$play_time)
    x <- as.vector(1:nrow(player_data))
    N <- length(y)
    the_data <- list("y" = y, "x" = x, "N" = N, 
                     "mu0" = 0, "g0" = 0.0001,
                     "mu1" = 0, "g1" = 0.0001,
                     "a" = 1, "b" = 1)
    
    initsfunction <- function(chain){
      .RNG.seed <- c(1,2)[chain]
      .RNG.name <- c("base::Super-Duper",
      "base::Wichmann-Hill")[chain]
      return(list(.RNG.seed=.RNG.seed,
                  .RNG.name=.RNG.name))
    }
    posterior <- run.jags(modelString,
                      n.chains = 1,
                      data = the_data,
                      monitor = c("beta0", "beta1", "sigma"),
                      burnin = 1000,
                      sample = 500,
                      thin = 1,
                      inits = initsfunction)
    beta1_vec <- posterior$mcmc[[1]][,2]
    id <- as.character(id)
    beta1_dist[,i] <- beta1_vec
    
  }
  colnames(beta1_dist) <- all_id
  return(beta1_dist)
}
```

```{r}
beta1_dist <- jags_on_all(all_players)
```

